---
title: "Exam Title"
author: "Professor Fantastic"
date: "February 23, 2017"
output:
  html_document:
    keep_md: yes
    theme: spacelab
  html_notebook: default
  word_document: default
---

```{r init, message=FALSE, warning=FALSE, include=FALSE}
library('dplyr')
```

```{r loadQuestions, message=FALSE, warning=FALSE, include=FALSE}
# Load questions
# The csv file should have the following fields: Question, Type, Points, CorrectAnswer
# For multiple-choice questions, additionally include: Lure1, Lure2, Lure3
# For questions with an associated image, additionally include: Image
# Also include any variables that you want to use to define the question order (e.g., Week)
questionsFile <- 'examquestions'
questions <- read.csv(paste0(questionsFile,'.csv'),stringsAsFactors=FALSE)

# Define a unique number for each separate version; this will set the randomization
seedNum <- 123  
set.seed(seedNum)

# Organize questions by week
# Could alternatively use this section to select out questions from a bigger pool using filter
questions$randomizer <- sample(nrow(questions))
questions %>%
  arrange(Week,randomizer) -> questions

# Summary info
numQs <- nrow(questions)
totalPoints <- sum(questions$Points)

```


**ID:** ___________________________    **Date:** ____________________  *v`r seedNum`*

This exam has `r numQs` questions. Make sure you complete every question. For multiple-choice questions, select the best answer. More than one may be somewhat correct, but one answer will be the “best” or most precise response to the question. For other questions, make sure to read the question closely. Some may ask for multiple pieces of information. Make sure to respond completely! Multiple-choice questions are worth two (2) points each, and true-false questions are worth one (1) point each. Other questions are graded as marked for a total of `r totalPoints` possible points.

---

```{r defineFormats, message=FALSE, warning=FALSE, include=FALSE}
# Define functions for formatting

# Multiple-choice with 4 randomized response options
formatMC <- function(q,qnum) {
  cat(qnum,'. ',q$Question,sep='')
  cat(' \n')
  cat(' \n')
  
  options <- c(q$CorrectAnswer,q$Lure1,q$Lure2,q$Lure3)
  randorder <- sample(4)
  cat('  \tA.',options[randorder[1]])
  cat('  \n')
  cat('  \tB.',options[randorder[2]])
  cat('  \n')
  cat('  \tC.',options[randorder[3]])
  cat('  \n')
  cat('  \tD.',options[randorder[4]])
  cat('  \n')

  optionLetters <- c('A','B','C','D')
  correct <- optionLetters[which(randorder==1)]
  
  return(correct)
}

# True/ false
formatTF <- function(q,qnum) {
  cat(qnum,'. *True or False:* ',q$Question,sep='')
  cat('  \t')
  cat(' Circle one: True / False')
  cat('  \n')

  correct <- q$CorrectAnswer
  
  return(correct)
}

# Short-answer
formatSA <- function(q,qnum) {
  cat(qnum,'. ',q$Question,' *(',q$Points,' points)*',sep='')
  cat('  \n')
  
  correct <- q$CorrectAnswer
  
  return(correct)
}

# Long-answer (same as short-answer but more space to write)
formatLA <- function(q,qnum) {
  cat(qnum,'. ',q$Question,' *(',q$Points,' points)*',sep='')
  cat('  \n')
  
  correct <- q$CorrectAnswer
  
  return(correct)
}

# Image-labels (for inserting image below question)
formatIL <- function(q,qnum) {
  cat(qnum,'. ',q$Question,' *(',q$Points,' points)*',sep='')
  cat('  \n')
  cat('![](',q$Image,')',sep='')
  cat('  \n')

  correct <- q$CorrectAnswer
  
  return(correct)
}

```

```{r presentQuestions, echo=FALSE, results="asis"}

# Loop through questions
# presenting them in the appropriate format and storing the correct answers
correct.all <- character(length=numQs)
order.all <- integer(length=numQs)
for (n in c(1:numQs)) {
  cat('  \n')
  q <- questions[n,]
  if (q$Type=="multiple-choice") {
    correct <- formatMC(q,n)
  } else if (q$Type=="short-answer") {
    correct <- formatSA(q,n)
  } else if (q$Type=="long-answer") {
    correct <- formatLA(q,n)
  } else if (q$Type=="T/F") {
    correct <- formatTF(q,n)
  } else if (q$Type=="image-labels") {
    correct <- formatIL(q,n)
  }
  correct.all[n] <- correct
  order.all[n] <- n
}

# End of exam
cat(' \n END OF EXAM')
```

```{r finishUp, echo=FALSE}

questions$Key <- correct.all
questions$Order <- order.all

# Simplify the question key
questions %>%
  select(Order,Points,Question,CorrectAnswer,Key) -> questions.key

# Write out questions file with key included
write.csv(questions.key,file=paste0(questionsFile,"_withkey_v",seedNum,".csv"))

```

